### 2019-10-22 Manuscript/pole_table_edited.tex
fix a few table references
small fixes to references
update table with Chuar poles

\begin{longtable}{p{1 in}p{1 in}rrrrrrrp{1.5 in}}
\toprule
                       terrane &                                        unit name & rating &  site lon &  site lat &  plon &  plat &  A$_{95}$ &                    age &                                     pole reference \\ \hline
\midrule
\endhead
\midrule
\multicolumn{10}{r}{{Continued on next page}} \\ \hline
\midrule
\endfoot

@@

             Laurentia-Wyoming &                       Sourdough mafic dike swarm &      A &    -108.3 &      44.7 & 292.0 &  49.2 &       8.1 &     1899$^{+5}_{-5}$ &                                 \cite{Kilian2016a} \\ \hline

@@

                     Laurentia &                                    Dubawnt Group &      B &     265.6 &      64.1 & 277.0 &   7.0 &       8.0 &   1785$^{+35}_{-35}$ &                                    \cite{Park1973} \\ \hline

@@

                     Laurentia &                                    Cleaver Dykes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741$^{+5}_{-5}$ &                                  \cite{Irving2004} \\ \hline

@@

                     Laurentia &                          Western Channel Diabase &      A &     242.2 &      66.4 & 245.0 &   9.0 &       6.6 &     1590$^{+3}_{-3}$ &                                  \cite{Irving1972} \\ \hline

@@

                     Laurentia &                        Ontario lamprophyre dykes &      A &     273.3 &      48.8 & 223.3 &  58.0 &       9.2 &   1143$^{+10}_{-10}$ &                                 \cite{Piispa2018a} \\ \hline

@@

                     Laurentia &                      Central Arizona diabases -N &      A &     249.2 &      33.7 & 175.3 &  15.7 &       7.0 &   1088$^{+11}_{-11}$ &                               \cite{Donadini2011a} \\ \hline

@@

                     Laurentia &                                  Gunbarrel dykes &      B &     248.7 &      44.8 & 129.4 &  13.9 &       8.2 &      778$^{+2}_{-2}$ &  Nordic workshop calculation based on data of \cite{Harlan1993a, Harlan1997a} \\ \hline
                     Laurentia &                                  Tsezotene Sills &      B &     235.0 &      63.5 & 137.8 &   1.6 &       5.0 &      778$^{+2}_{-2}$ &                                   \cite{Park1989a} \\ \hline
                     Laurentia &                             Uinta Mountain Group &      B &     250.7 &      40.8 & 161.3 &   0.8 &       4.7 &    775$^{+25}_{-25}$ &                                   \cite{Weil2006a} \\ \hline
            Laurentia-Svalbard &                        Svanbergfjellet Formation &      B &      18.0 &      78.5 & 226.8 &  25.9 &       5.8 &    760$^{+30}_{-30}$ &                                 \cite{Maloof2006a} \\ \hline
                     Laurentia &                        Franklin event grand mean &      A &     275.4 &      73.0 & 162.1 &   6.7 &       3.0 &      724$^{+3}_{-3}$ &                               \cite{Denyszyn2009a} \\ \hline

>>>>

\begin{longtable}{p{1 in}p{1 in}rrrrrrrp{1.5 in}}
\toprule
                       terrane &                                        unit name & rating &  site lon (\textdegree) &  site lat (\textdegree) &  plon (\textdegree) &  plat (\textdegree) &  A$_{95}$ &                    age (Ma)&                                     pole reference \\ \hline
\midrule
\endhead
\midrule
\multicolumn{10}{r}{{Continued on next page}} \\ \hline
\midrule
\endfoot

@@

             Laurentia-Wyoming &                       Sourdough mafic dike swarm &      A &    -108.3 &      44.7 & 292.0 &  49.2 &       8.1 &     1899$^{+5}_{-5}$ &                                 \cite{Kilian2016b} \\ \hline

@@

                     Laurentia &                                    Dubawnt Group &      B &     265.6 &      64.1 & 277.0 &   7.0 &       8.0 &   1785$^{+35}_{-35}$ &                                    \cite{Park1973a} \\ \hline

@@

                     Laurentia &                                    Cleaver Dykes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741$^{+5}_{-5}$ &                                  \cite{Irving2004a} \\ \hline

@@

                     Laurentia &                          Western Channel Diabase &      A &     242.2 &      66.4 & 245.0 &   9.0 &       6.6 &     1590$^{+3}_{-3}$ &                                 \cite{Irving1972a} \\ \hline

@@

                     Laurentia &                        Ontario lamprophyre dykes &      NR &     273.3 &      48.8 & 223.3 &  58.0 &       9.2 &   1143$^{+10}_{-10}$ &                                 \cite{Piispa2018a} \\ \hline

@@

                     Laurentia &                      Central Arizona diabases -N &      A &     249.2 &      33.7 & 175.3 &  15.7 &       7.0 &   1088$^{+11}_{-11}$ &                               \cite{Donadini2011b} \\ \hline

@@

            Laurentia &                                  Gunbarrel dykes &      B &     248.7 &      44.8 & 138.2 &   9.1 &      12.0 &      778$^{+2}_{-2}$ &  Calculation from \cite{Eyster2019a} based on data of \cite{Harlan1993a, Harlan1997a}  \\ \hline
   Laurentia-Svalbard &                        Svanbergfjellet Formation &      B &      18.0 &      78.5 & 226.8 &  25.9 &       5.8 &    770$^{+19}_{-40}$ &                                 \cite{Maloof2006a} \\ \hline
            Laurentia &                             Uinta Mountain Group &      B &     250.7 &      40.8 & 161.3 &   0.8 &       4.7 &     760$^{+6}_{-10}$ &                                   \cite{Weil2006b} \\ \hline
            Laurentia &                                    Carbon Canyon &     NR &     248.2 &      36.1 & 166.0 &  -0.5 &       9.7 &      757$^{+7}_{-7}$ &  \cite{Weil2004a} as calculated in \cite{Eyster2019a} \\ \hline
            Laurentia &                             Carbon Butte/Awatubi &     NR &     248.5 &      35.2 & 163.8 &  14.2 &       3.5 &      751$^{+8}_{-8}$ &                                 \cite{Eyster2019a} \\                   Laurentia &                        Franklin event grand mean &      A &     275.4 &      73.0 & 162.1 &   6.7 &       3.0 &      724$^{+3}_{-3}$ &                               \cite{Denyszyn2009a} \\ \hline
